### 2021-05-04 cv/cv-body.tex
Update CV
Add DOI

\begin{description}
\tightlist
\item[2021]
Stockdale, J.E., \textbf{Anderson, S.C.}, Edwards, A.M., Iyaniwura,
S.A., Mulberry, N., Otterstatter, M.C., Janjua, N.Z., Coombs, D.,
Colijn, C., and Irvine, M.A.\ 2021. Quantifying transmissibility of
COVID-19 and impact of intervention within long-term health care
facilities. medRxiv: 2021.02.01.21249903.
\url{https://doi.org/10.1101/2021.02.01.21249903}.
\item[2020]
\textbf{Anderson, S.C.}, Mulberry, N., Edwards, A.M., Stockdale, J.E.,
Iyaniwura, S.A., Falcao, R.C., Otterstatter, M.C., Janjua, N.Z., Coombs,
D., and Colijn, C. 2020. How much leeway is there to relax COVID-19
control measures? medRxiv 2020.06.12.20129833.
\url{https://doi.org/10.1101/2020.06.12.20129833}.
\end{description}

@@

@@

\textbf{Anderson, S.C.}, P.R. Elsen, B.B. Hughes, R.K. Tonietto, M.C.
Bletz, D.A. Gill, M.A.\ Holgerson, S.E. Kuebbing, C. McDonough MacKenzie,
M.H. Meek, D. Veríssimo. Trends in ecology and conservation over eight
decades. In press at Frontiers in Ecology and the Environment.

>>>>

\begin{description}
\tightlist
\item[2021]
English, P., E.J. Ward, C.N. Rooper, R.E. Forrest, L.A. Rogers, K.L.
Hunter, A.M. Edwards, B.M. Connors, S.C. Anderson. Contrasting climate
velocity impacts in warm and cool locations: A meta-analysis across 38
demersal fish species in the northeast Pacific. EcoEvoRxiv.
\url{https://doi.org/10.32942/osf.io/b87ng}.
\item[2021]
Stockdale, J.E., \textbf{Anderson, S.C.}, Edwards, A.M., Iyaniwura,
S.A., Mulberry, N., Otterstatter, M.C., Janjua, N.Z., Coombs, D.,
Colijn, C., and Irvine, M.A.\ Quantifying transmissibility of COVID-19
and impact of intervention within long-term health care facilities.
medRxiv: 2021.02.01.21249903.
\url{https://doi.org/10.1101/2021.02.01.21249903}.
\end{description}

@@

\begin{description}
\tightlist
\item[2021]
Freshwater C., \textbf{S.C. Anderson}, T.D. Beacham, W. Luedke, C. Wor,
J. King. An integrated model of seasonal changes in stock composition
and abundance with an application to Chinook salmon. PeerJ 9:e11163.
\url{https://doi.org/10.7717/peerj.11163}.
\item[2021]
\textbf{Anderson, S.C.}, P.R. Elsen, B.B. Hughes, R.K. Tonietto, M.C.
Bletz, D.A. Gill, M.A.\ Holgerson, S.E. Kuebbing, C. McDonough MacKenzie,
M.H. Meek, D. Veríssimo. Trends in ecology and conservation over eight
decades. In press at Frontiers in Ecology and the Environment.
\url{http://doi.org/10.1002/fee.2320}.
\item[2021]
\textbf{Anderson, S.C.}, Mulberry, N., Edwards, A.M., Stockdale, J.E.,
Iyaniwura, S.A., Falcao, R.C., Otterstatter, M.C., Janjua, N.Z., Coombs,
D., and Colijn, C. 2020. How much leeway is there to relax COVID-19
control measures? In press at Epidemics.
\url{https://doi.org/10.1016/j.epidem.2021.100453}.
\end{description}

@@
